### 2015-12-17 WRITEUP/Obs.tex
minor updates

\section{Observations}
\subsection{PdBI} \label{sec:PdBIdata}
Observations of the CO($J$ = 2 $\rightarrow$ 1) rotational line ($\nu_{\rm rest}$ = 230.5379938 GHz) toward the background galaxy RXJ1131-1231 at $z$ = 0.655BLAH
 were carried out using IRAM Plateau de Bure Interferometer (PdBI) at the redshifted frequency of $\nu_{\rm obs}$ = 
 BLAH GHz (BLAH mm) (Program ID: S14BX001; PI: D. Riechers). 
 Two observing runs were carried out on 2014 Dec 06 and 2015 Feb 05 under excellent / GOOD? 
%2 mm
weather conditions in the C and D array configurations, respectively. The 2 mm receivers were used to cover the redshifted CO($J$ = 2 $\rightarrow$ 1) line and the underlying continuum emission (rest frame BLAH = (2.152 * (1+z)) mm), employing a correlator setup providing an effective bandwidth of 3.16 GHz and spectral resolution of 10.0 MHz ($\sim$21.5281 km s$^{-1}$).
This resulted in 2.2 hours and 1.5 hours of six antenna-equivalent on-source time 
HOW TO FIND OUT TIME AFTER DISCARD DATA
after discarding unusable visibility data for C and D array observations, respectively.
% D: 1.5 hours; 1055+018 , 3C279 (RF, fixed flux), 1127-145 (phase/amp), 1124-106(ditto)
% C: 2.2 hours; MWC349 (fixed flux), 1055+018 (RF = bandpass), 1124-186 (phase/amp), 1127-145 (ditto)
% total: 3.75 hours
%For both tracks, 
The nearby quasars 1127$-$145 and 1124$-$186 were observed every BLAH minutes for
pointing, secondary amplitude, and phase calibration, and MWC349 was observed as the primary
absolute flux calibrator for C array observations.
The nearby quasars 1127$-$145 and 1124$-$106 were observed every BLAH minutes for
pointing, secondary amplitude, and phase calibration, and 3C279 was observed as the primary
absolute flux calibrator for D array observations.
1055$+$018 and 3C279 were observed as bandpass calibrators for C and D array observations, respectively, yielding $\lesssim
$15\% calibration accuracy.

@@

\subsection{CARMA} \label{sec:carmadata}
Observations of the CO($J$ = 3 $\rightarrow$ 2) rotational line ($\nu_{\rm rest}$ = 345.7959899 GHz) toward the background galaxy RXJ1131-1231 at $z$ = 
0.655BLAH 
 were carried out using the Combined Array for Research in Millimeter-wave Astronomy (CARMA) at the redshifted frequency of $\nu_{\rm obs}$ = BLAH GHz (BLAH mm) (Program ID: BLAH; PI: D. Riechers).
Two observing runs were carried out on 2013 April 27 and Jun 09 under excellent 3 mm weather conditions in the C and D array configurations, respectively. The 3 mm receivers were used to cover the redshifted CO($J$ = 3 $\rightarrow$ 2) line, employing a correlator setup providing a bandwidth of 3.75 GHz in each sideband and spectral resolution of 5.208 MHz ($\sim$17 km s$^{-1}$). The line was placed in the
upper sidebands for both tracks with the local oscillator tuned to $\nu_{\rm LO}\sim$ 90.7 GHz; this resulted in 1.9 hours and 2.6 hours of 15 antenna-equivalent on-source time after discarding unusable visibility data for C and D array observations, respectively.

For both tracks, the nearby radio quasar J1310+323 was observed every 15 minutes for
pointing, amplitude, and phase calibration, and MWC349 was observed as the primary
absolute flux calibrator. J1337$-$129 and 3C273 were observed as bandpass calibrators for C and D array observations, respectively, yielding $\sim
$15\% calibration accuracy.
The MIRIAD package was used to calibrate and analyze the visibility data which are imaged and deconvolved using
the CLEAN algorithm with ``natural" weighting. This yields a synthesized clean beam size of 2$\farcs$6 $\times$ 2\farcs2 for the upper sideband image cube. The final rms noise is $\sigma$ = 0.68 Jy km s$^{-1}$ beam$^{-1}$ over a channel width of 208.3 MHz (corresponding to 687 km s$^{-1}$). % one bin is 83.195 km s$^{-1}$
The continuum image is created by
averaging over all the line-free channels ($\nu_{\rm cont}\sim$90.7 GHz). This yields a synthesized clean beam size of 3\farcs5 $\times$ 3\farcs0 and an rms noise of 0.24 mJy beam$^{-1}$.

>>>>

\section{Observations}
\subsection{PdBI} \label{sec:PdBIdata}
Observations of the CO($J$ = 2 $\rightarrow$ 1) rotational line ($\nu_{\rm rest}$ = 230.5379938 GHz) toward the background galaxy RXJ1131-1231 at $z$ = 0.655BLAH
 were carried out using IRAM Plateau de Bure Interferometer (PdBI) at the redshifted frequency of $\nu_{\rm obs}$ = 
 BLAH GHz (BLAH mm) (Program ID: S14BX001; PI: D. Riechers). 
 Two observing runs were carried out on 2014 Dec 06 and 2015 Feb 05 under excellent / GOOD? 
%2 mm
weather conditions in the C and D array configurations, respectively. The 2 mm receivers were used to cover the redshifted CO($J$ = 2 $\rightarrow$ 1) line and the underlying continuum emission (rest frame BLAH = (2.152 * (1+z)) mm), employing a correlator setup providing an effective bandwidth of 3.16 GHz and spectral resolution of 10.0 MHz ($\sim$21.5281 km s$^{-1}$).
This resulted in 3.74 hours of cumulative six antenna-equivalent on-source time 
after discarding unusable visibility data.
% D: 1.5 hours; 1055+018 , 3C279 (RF, fixed flux), 1127-145 (phase/amp), 1124-106(ditto)
% C: 2.2 hours; MWC349 (fixed flux), 1055+018 (RF = bandpass), 1124-186 (phase/amp), 1127-145 (ditto)
% total: 3.75 hours
%For both tracks, 
The nearby quasars 1127$-$145 and 1124$-$186 were observed every BLAH minutes for
pointing, secondary amplitude, and phase calibration, and MWC349 was observed as the primary
absolute flux calibrator for C array observations.
The nearby quasars 1127$-$145 and 1124$-$106 were observed every BLAH minutes for
pointing, secondary amplitude, and phase calibration, and 3C279 was observed as the primary
absolute flux calibrator for D array observations.
1055$+$018 and 3C279 were observed as bandpass calibrators for C and D array observations, respectively, yielding $\lesssim
$15\% calibration accuracy.

@@

\subsection{CARMA} \label{sec:carmadata}
% LO = 215.6694 Ghz
% 3C273 FG
% 3C279 Bandpass
% mars flux
% after flagging: Total observing time is  1.48 hours, checked with uvindex
%
Observations of the CO($J$ = 3 $\rightarrow$ 2) rotational line ($\nu_{\rm rest}$ = 345.7959899 GHz) toward the background galaxy RXJ1131-1231 at $z$ = 
0.655BLAH 
 were carried out using the Combined Array for Research in Millimeter-wave Astronomy (CARMA) at the redshifted frequency of $\nu_{\rm obs}$ = BLAH GHz (BLAH mm) (Program ID: cf0098; PI: D. Riechers).
observations were carried out on 2014 February 17 under good 3 mm weather conditions in the D array configurations. The 3 mm receivers were used to cover the redshifted CO($J$ = 3 $\rightarrow$ 2) line, employing a correlator setup providing a bandwidth of 3.75 GHz in each sideband and spectral resolution of 12.5 MHz ($\sim$17BLAH km s$^{-1}$). The line was placed in the
lower sidebands with the local oscillator tuned to $\nu_{\rm LO}\sim$ 216 GHz; this resulted in 1.5 hours of 15 antenna-equivalent on-source time after discarding unusable visibility data.

The nearby radio quasar 3C273 was observed every 15 minutes for
pointing, amplitude, and phase calibration, and Mars was observed as the primary
absolute flux calibrator. 3C279 was observed as bandpass calibrators, yielding $\sim
$15\%BLAH calibration accuracy.
The MIRIAD package was used to calibrate and analyze the visibility data which are imaged and deconvolved using
the CLEAN algorithm with ``natural" weighting. This yields a synthesized clean beam size of 3\farcs1 $\times$ 1\farcs9 for the lower sideband image cube. The final rms noise is $\sigma$ = BLAH Jy km s$^{-1}$ beam$^{-1}$ over a channel width of BKAH MHz (corresponding to BLAH km s$^{-1}$). 
The continuum image is created by
averaging over all the line-free channels ($\nu_{\rm cont}\sim$216 GHz). This yields a synthesized clean beam size of Blah\farcs5 $\times$ blah\farcs0 and an rms noise of 0.24Blah mJy beam$^{-1}$.
